### 2011-06-20 papers/GPUScA-2011/intro.tex
Copied IPDPS 2011 paper to GPUScA 2011 workshop (in Galveston)

Similar whole array shifting was used in higher dimensions for finite
different codes within the computational physics community, especially
at Los Alamos for codes targeting the CM-5 system that resided there until the
late 1990s.  A body of research in compilation of stencil-based codes
that use shift operators targeting these systems is related to the
work we present here~\cite{stencil-compiler}.

>>>>

Similar whole array shifting was used in higher dimensions for finite
difference codes within the computational physics community, especially
at Los Alamos for codes targeting the CM-5 system that resided there until the
late 1990s.  A body of research in compilation of stencil-based codes
that use shift operators targeting these systems is related to the
work we present here~\cite{stencil-compiler}.
